%-------------------------
% Resume in Latex (Inspired by https://github.com/sb2nov/resume)
% Author : Rishabh Tatia
% Website: https://tatiaris.com/docs/resume.tex
% License : MIT
%------------------------

\documentclass[letterpaper,hidelinks,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}\\}
}
\newcommand{\resumeEducationItem}[2]{
  \item[]\small{
    \textbf{#1}{: #2 \vspace{-2pt}}\\
  }
}

\newcommand{\resumeEducationSubheading}[4]{
  \vspace{2pt}\item[]
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} -- #2 & #3\\
      \textit{#4}\\
    \end{tabular*}
}

\newcommand{\resumeProjectSubheading}[3]{
  \vspace{2pt}\item[]
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} -- \textit{#2} & #3\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeAwardSubheading}[4]{
  \vspace{2pt}\item[]
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} -- #2 -- \textit{#3} & #4\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item[]
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} -- \textit{#2} -- #3 & #4\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0em]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeEducationItemListStart}{\begin{itemize}[leftmargin=0em]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://tatiaris.com/}{\Large RISHABH TATIA}} & \textit{\href{https://github.com/tatiaris}{github.com/tatiaris}}\\
  \href{mailto:tatiaris2001@gmail.com}{tatiaris2001@gmail.com} / +1-713-208-0982 / \textit{\href{https://tatiaris.com}{tatiaris.com}} & \textit{\href{https://linkedin.com/in/tatiaris}{linkedin.com/in/tatiaris}}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationSubheading
      {TEXAS A\&M UNIVERSITY}{College Station, TX}{Aug 2018 -- May 2022}
      {Bachelor of Science in Computational Mathematics; Minor in Computer Science}
      \resumeEducationItemListStart
        \resumeEducationItem{Technical Skills}
          {AWS, Firebase, Git, Node.js, Spring Boot, ReactJS, React Native, TypeScript, Java, Python, C++.}
        \resumeEducationItem{Relevant Coursework}
          {Algorithm Design and Analysis, Data Structures and Algorithms, Discrete Mathematics.}
        \resumeEducationItem{Certifications}
          {\textit{\href{https://www.hackerrank.com/certificates/831932b062b2}{JavaScript (Intermediate)}, \href{https://www.hackerrank.com/certificates/a8a9d2d37735}{Node.js (Intermediate)},
          \href{https://www.hackerrank.com/certificates/acc5ef4e253e}{Problem Solving (Intermediate)}}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {INTUIT}{Software Engineering Intern}{San Diego, CA}{May 2021 - Aug 2021}
      \resumeItemListStart
        \resumeItem
          {Refactored and enhanced the backend powering the Finish and File section in Turbotax utilizing Spring Boot and Java.}
        \resumeItem
          {Devised and extended libraries to improve server side rendering and server-driven UI functionality for TurboTax Online.}
        \resumeItem
          {Enhanced front-end plugins and widgets used to guide users on Turbotax using React, Redux, and Lottie.}
        \resumeItem
          {Worked in an Agile environment with a Jira ticketing system to monitor projects and ensure timely delivery of value.}
      \resumeItemListEnd

    \resumeSubheading
      {TAMU DATATHON}{Tech Lead}{College Station, TX}{May 2020 - Present}
      \resumeItemListStart
        \resumeItem
          {Organized one of largest MLH Datathon events with 1000+ applicants, spanning 100+ majors, and 120+ universities.}
        \resumeItem
          {Lead two teams of engineers to enhance the online presence and build the challenges platform for the event.}
        \resumeItem
          {Constructed Portal, an event showcase and participation platform combined with user tracking, with Node.js and React.}
        \resumeItem
          {Developed Mercury, a mailing web application consolidated with Mailgun to edit, view, and send custom HTML emails.}
      \resumeItemListEnd

    \resumeSubheading
      {ACELAB}{Full Stack Developer}{College Station, TX}{Feb 2020 - Present}
      \resumeItemListStart
        \resumeItem
          {Designed and updated webpages for easier access to information and better user experience through HTML, JS, and CSS.}
        \resumeItem
          {Created WIEAT, a web-based data entry, visualization, and analysis application leveraging the Next.js framework.}
        \resumeItem
          {Applied best strategies for improving Acelab's online presence, boosting visitor count to 12,000+ users per year.}
      \resumeItemListEnd
      
    \resumeSubheading
      {4.0 TUTORING}{PHP Developer}{College Station, TX}{Aug 2019 - Jan 2020}
      \resumeItemListStart
        \resumeItem
          {Devised a work logging platform with authentication to keep track of employee performance utilizing PHP and SQL.}
        \resumeItem
          {Assisted in boosting tutoring sales by 7\% over one semester by implementing a more efficient workflow for students.}
        \resumeItem
          {Redesigned webpages to provide better SEO, responsiveness and user friendliness with HTML, JS, and CSS.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectSubheading
      {RESUVILLE}{\href{https://resuville.com}{resuville.com}}{Dec 2020 - May 2021}{}
      \resumeItemListStart
        \resumeItem
          {Developed and launched a free and user friendly resume builder website for efficient templating with Node.js and React.}
        \resumeItem
          {Integrated sign up / log in functionality into the app leveraging Auth0 and data storage and tracking through MongoDB.}
        \resumeItem
          {Implemented a searching and filtering system, along with intricate customization for all available templates.}
      \resumeItemListEnd
    
    \resumeProjectSubheading
      {INTERACTIVE EPISODE ANALYSIS TOOL}{\href{https://wieat.vercel.app/}{wieat.vercel.app}}{Oct 2020 - Mar 2021}{}
      \resumeItemListStart
        \resumeItem
          {Invented and published a data entry, visualization, and analysis tool to perform interactive episode analysis.}
        \resumeItem
          {Automated tedious process of data collection through a public Node.js API, enhancing research efficiency.}
        \resumeItem
          {Employed MongoDB to create a centralized database for all interactions and episodes for collective data analysis.}
      \resumeItemListEnd
    
    \resumeProjectSubheading
      {AGGIE DEGREE PLANNER}{\href{https://tamudp.vercel.app/}{tamudp.vercel.app}}{Nov 2020 - Dec 2020}{}
      \resumeItemListStart
        \resumeItem
          {Constructed and deployed a generalized university degree planner application employing the Next.js framework.}
        \resumeItem
          {Used Axios and Cheerio to scrape major relevant courses and generate a database of graduation requirements.}
        \resumeItem
          {Designed React components to integrate progress tracking for students to conveniently check degree progression.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%
%--------AWARDS------------
\section{Awards}
 \resumeSubHeadingListStart
    \resumeAwardSubheading
      {First Overall, Google Cloud Challenge}{TAMUHack 2022}{\href{https://devpost.com/software/rekkme}{devpost.com/software/rekkme}}{Jan 2022}
      \resumeItemListStart
        \resumeItem
          {Developed Rekkme, a social platform that aims to help people recommend and discover elements in several categories.}
        \resumeItem
          {Built a recommendation classifier and tag generator to classify various recommendations into their respective categories.}
        \resumeItem
          {Designed the UI/UX and implemented a smooth recommending process by making the website a progressive web app.}
      \resumeItemListEnd
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
